Title Text\titlenote{with optional title note}

### 2017-07-27 sigplanconf-template.tex
Early Design Section added

\section{Introduction}
	Understanding how a software system works is important in designing, implementing, and using it. Software architecture can be defined as the “fundamental organization of a system embodied in its components, their relations to each other, and the environment.” Any system, including a living organism can be understood from different perspectives and views; a human being can be analyzed in terms of his or her comprising systems as in the cardiovascular system or nervous system, or as a part of a larger structure, like a friendship, society, or species.

@@

>>>>

\section{Introduction}

	Understanding how a software system works is important in designing, implementing, and using it. Software architecture can be defined as the “fundamental organization of a system embodied in its components, their relations to each other, and the environment.” Any system, including a living organism can be understood from different perspectives and views; a human being can be analyzed in terms of his or her comprising systems as in the cardiovascular system or nervous system, or as a part of a larger structure, like a friendship, society, or species.

@@

\section{Early Design}

	As a solution to the issue of carrying intended architecture guarantees through to the final implementation, we present Trinity, an extension to the Wyvern programming language that aims to make software architecture views a presecriptive, rather than simply descriptive, aspect of a software system in Wyvern. Trinity incorporates architecture in a unique way, making it a “live” component: software systems can have hard-coded architectures for all three architecture views. Instead of providing a descriptive architecture that attempts to explain how a system functions, Trinity supports architecture as a language construct in Wyvern. In the case of the CnC architectural view, what would conventionally be only logical organizations and distinctions between components and connectors, can now be actually implemented components and connectors. Since Trinity supports prescriptive software architecture views it allows developers to catch architecture-related errors at compile time, rather than runtime. This novel ability enables safer inspection for vulnerabilities originating in architecture flaws.
